embedplyr: Tools for Working With Text Embeddings

### 2025-09-01 README.Rmd
consistency in linking to reference documentation
addresses issue #9
change `predict.embeddings()` to `emb()`
addresses issue #6

The outcome is an embeddings object. An embeddings object is just a numeric matrix with fast hash table indexing by rownames (generally tokens). This means that it can be easily coerced to a dataframe or tibble, while also allowing special embeddings-specific methods and functions, such as `predict.embeddings()` and `find_nearest()`:

```{r}
moral_embeddings <- predict(glove_twitter_25d, c("good", "bad"))
moral_embeddings

@@

```{r}
good_vec <- predict(glove_twitter_25d, "good")
intense_vec <- predict(glove_twitter_25d, "intense")
valence_quantified <- valence_embeddings_df |> 
	get_sims(
		dim_1:dim_25, 
		list(
			good = good_vec, 
			intense = intense_vec
			)
		)
valence_quantified
```
### Example Quanteda Workflow

@@

```{r}
new_embeddings <- predict(glove_twitter_25d, c("new", "strange"))

@@

Aligning separately trained embeddings can be useful for tracking semantic change over time or semantic differences between training datasets. It can also be useful for comparing texts across languages. `align_embeddings(x, y)` rotates the embeddings in `x` (and changes their dimensionality if necessary) so that they can be compared with those in `y`. Optionally, `matching` can be used to specify one-to-one matching between  embeddings in the two models (e.g. a bilingual dictionary).

>>>>

The outcome is an embeddings object. An embeddings object is just a numeric matrix with fast hash table indexing by rownames (generally tokens). This means that it can be easily coerced to a dataframe or tibble, while also allowing special embeddings-specific methods and functions, such as `emb()` and `find_nearest()`:

```{r}
moral_embeddings <- emb(glove_twitter_25d, c("good", "bad"))
moral_embeddings

@@

```{r}
good_vec <- emb(glove_twitter_25d, "good")
intense_vec <- emb(glove_twitter_25d, "intense")
valence_quantified <- valence_embeddings_df |> 
	get_sims(
		dim_1:dim_25, 
		list(
			good = good_vec, 
			intense = intense_vec
			)
		)
valence_quantified
```
### Example Quanteda Workflow

@@

```{r}
new_embeddings <- emb(glove_twitter_25d, c("new", "strange"))

@@

Aligning separately trained embeddings can be useful for tracking semantic change over time or semantic differences between training datasets. It can also be useful for comparing texts across languages. `align_embeddings(x, y)` rotates the embeddings in `x` (and changes their dimensionality if necessary) so that they can be compared with those in `y`. Optionally, `matching` can be used to specify one-to-one matching between  embeddings in the two models (e.g. a bilingual dictionary). See `align_embeddings()` for full documentation.

### 2025-09-01 paper/paper.Rmd
change `predict.embeddings()` to `emb()`
addresses issue #6

The output of `load_embeddings()` is an embeddings object. An embeddings object is simply a numeric matrix with fast hash table indexing by rownames (generally tokens). This means that it can be easily coerced to a dataframe or tibble, while also allowing special embeddings-specific methods and functions, such as `predict.embeddings()` and `find_nearest()`:

```{r}
moral_embeddings <- predict(glove_twitter_25d, c("good", "bad"))
moral_embeddings

@@

# embed dictionaries
high_anx_dict_embeddings <- predict(glove_twitter_25d, high_anx_dict)
low_anx_dict_embeddings <- predict(glove_twitter_25d, low_anx_dict)

>>>>

The output of `load_embeddings()` is an embeddings object. An embeddings object is simply a numeric matrix with fast hash table indexing by rownames (generally tokens). This means that it can be easily coerced to a dataframe or tibble, while also allowing special embeddings-specific methods and functions, such as `emb()` and `find_nearest()`:

```{r}
moral_embeddings <- emb(glove_twitter_25d, c("good", "bad"))
moral_embeddings

@@

# embed dictionaries
high_anx_dict_embeddings <- emb(glove_twitter_25d, high_anx_dict)
low_anx_dict_embeddings <- emb(glove_twitter_25d, low_anx_dict)
